A pipeline to analyse time-course gene expression data

### 2020-09-02 manuscript.tex
Deploy NelleV/2019timecourse-rnaseq-pipeline to github.com/NelleV/2019timecourse-rnaseq-pipeline.git:gh-pages

Before performing any additional exploratory analysis, let us only keep highly
variable genes: for this step, we keep only the top 50\% most variable genes.

@@

The number of genes found differentially expressed ranges from around 12000 to
29000 depending on the strain and dosage of influenza virus given to the mice.
This corresponds to between 30\% to 70\% of the genes found differentially
expressed in this time-course experiment.

@@

We then use the \texttt{plot\_splines\_data} function, only now applied to the centroids, to visualize the centroids of
each cluster obtained with the splines k-means model.

@@

{\centering \includegraphics[width=.5\textwidth,]{reports/manuscript_files/figure-latex/unnamed-chunk-18-1}

\caption{K-means centroids}\label{fig:unnamed-chunk-18}
\end{figure}

>>>>

Before performing any additional exploratory analysis, let us only keep highly
variable genes: for this step, we keep only the top 50\% most variable genes.
In Figure \ref{fig:geneVarHist}, we plot the distribution of variance across
all genes.

@@

The number of genes found differentially expressed ranges from around 12000 to
29000 depending on the strain and dosage of influenza virus given to the mice
(Figure \ref{deTimeDist}).
This corresponds to between 30\% to 70\% of the genes found differentially
expressed in this time-course experiment.

@@

We then use the \texttt{plot\_splines\_data} function, only now applied to the
centroids, to visualize the centroids of each cluster obtained with the
splines k-means model (Figure \ref{fig:centroids}).

@@

{\centering \includegraphics[width=.5\textwidth,]{reports/manuscript_files/figure-latex/centroids-1}

\caption{K-means centroids}\label{fig:centroids}
\end{figure}
